Predictors of frog survival following translocations - supplemental analyses

### 2022-12-13 code/translocation_survival_analysis_suppl.Rmd
Add calculations of viability model parameters

## Evaluate effect of frog size independent of donor populationRead in frog translocation dataset

@@

>>>>

## Evaluate effect of frog size independent of donor population

@@

## Calculate parameters for viability analysis

### Load packages

```{r}
library(RPostgreSQL)
library(lubridate)
library(dplyr)
library(magrittr)
library(readr)
```

### Estimate subadult survival

#### Connect to database

-   Use 2nd chunk when connecting via SSH.

-   Users without credentials to access database can start with `subadult_survival.csv` saved below.

```{r}
con = dbConnect(dbDriver("PostgreSQL"),
                host = Sys.getenv("host"), 
                port = Sys.getenv("port"), 
                dbname = Sys.getenv("dbname"),
                user = rstudioapi::askForPassword("user name"),
                password = rstudioapi::askForPassword("password")
               )
```

```{r}
con = dbConnect(dbDriver("PostgreSQL"),
                host = "localhost",
                port = 15432,
                dbname = Sys.getenv("dbname"), 
                user = rstudioapi::askForPassword("user name"),
                password = rstudioapi::askForPassword("password")
                )
```

#### Retrieve Bd data for translocated frogs from database

-   Used 70550 because of its long and relatively intensive survey history.

```{sql, connection=con, output.var="surv"}
select
  site_id,
  visit_date,
  species,
  visual_life_stage,
  visual_animal_state,
  count
from visit
inner join survey on visit_id = visit.id
inner join visual_survey on survey_id = survey.id  
where site_id in (70550) and
  species = 'ramu' and
  visual_life_stage = 'subadult' and
  visual_animal_state = 'alive'
order by site_id, visit_date
```

#### Disconnect from database

#### Save raw dataset

```{r}
surv %>% write_csv(here::here("data", "raw", "subadult_survival.csv"))
```

#### Calculate maximum annual counts

```{r}
surv <- surv %>% 
  group_by(visit_date) %>% 
  summarize(count_sum = sum(count)) %>% 
  ungroup() %>% 
  mutate(year = year(visit_date)) %>% 
  group_by(year) %>% 
  summarize(count_max = max(count_sum))
```

#### Extract number of new recruits from mrmr model

```{r}
model <- read_rds(here::here("data", "clean", "70550_model.rds"))

get_numeric_indices <- function(string) {
  idx_mat <- stringr::str_extract_all(string, "[0-9]+", simplify = TRUE)
  colnames(idx_mat) <- paste0("index_", seq_len(ncol(idx_mat)))
  tibble::as_tibble(idx_mat) %>%
    dplyr::mutate_all(readr::parse_integer)
}

survey_prim_periods <- model$data$surveys %>%
  group_by(.data$primary_period) %>%
  filter(.data$secondary_period == min(.data$secondary_period)) %>% 
  ungroup()

p <- model$m_fit$draws("B", format = "draws_df") %>%
  tidyr::pivot_longer(tidyselect::starts_with("B")) %>%
  suppressWarnings() %>%
  mutate(
    get_numeric_indices(.data$name),
    primary_period = .data$index_1 + 1
  ) %>%
  group_by(.data$primary_period) %>%
  summarize(lo = quantile(.data$value, .025),
            med = median(.data$value),
            hi = quantile(.data$value, .975),
            .groups = "drop") %>%
  left_join(survey_prim_periods, by = "primary_period")

recruit <- p %>% 
  group_by(year) %>% 
  summarize(recruit_sum = sum(med))
```

#### Create final dataset

```{r}
subadult_survival <- surv %>% 
  inner_join(recruit, by = c("year"))
```

#### Calculate subadult survival

-   Assumes that p(detection) for subadults is 0.25.

```{r}
subadult_sum <- subadult_survival %>% 
  filter(between(year, 2008, 2020)) %>% 
  summarize(sum(count_max))

recruit_sum <- subadult_survival %>% 
  filter(between(year, 2009, 2021)) %>% 
  summarize(sum(recruit_sum))

survival_sub <- recruit_sum / (subadult_sum * 4) 
```

### Estimate 1st-year tadpole survival

-   Used 74976 due to its shallow habitats that allow accurate tadpole counts.

-   1st-year tadpole counts are from field notebooks.

```{r}
surv_tad <- tibble(site_id = 74976, year = 2019:2021, count = c(250, 300, 305))
```

#### Extract adult abundance from mrmr model

-   Used minimum survey date per year to estimate number of females during breeding season.

```{r}
model <- read_rds(here::here("data", "clean", "74976_model.rds"))

get_numeric_indices <- function(string) {
  idx_mat <- stringr::str_extract_all(string, "[0-9]+", simplify = TRUE)
  colnames(idx_mat) <- paste0("index_", seq_len(ncol(idx_mat)))
  tibble::as_tibble(idx_mat) %>%
    dplyr::mutate_all(readr::parse_integer)
}

survey_prim_periods <- model$data$surveys %>%
  group_by(.data$primary_period) %>%
  filter(.data$secondary_period == min(.data$secondary_period)) %>% 
  ungroup()

p <- model$m_fit$draws("N", format = "draws_df") %>%
        tidyr::pivot_longer(tidyselect::starts_with("N")) %>%
        suppressWarnings() %>%
        mutate(
          get_numeric_indices(.data$name),
          primary_period = .data$index_1 + 1
        ) %>%
        group_by(.data$primary_period) %>%
        summarize(lo = quantile(.data$value, .025),
                  med = median(.data$value),
                  hi = quantile(.data$value, .975),
                  .groups = "drop") %>%
        left_join(survey_prim_periods, by = "primary_period")

abund_ad <- p %>% 
  group_by(year) %>% 
  summarize(survey_date = min(survey_date)) %>%
  select(survey_date) %>% 
  inner_join(p, by = c("survey_date")) %>% 
  select(year, med)
```

#### Create final dataset

```{r}
surv_tad <- surv_tad %>% 
  inner_join(abund_ad, by = "year") %>% 
  rename(adults = med)
```

#### Calculate tadpole survival

-   Assumptions:

    -   p(detection) for 1st-year tadpoles is 0.5.

    -   \# females is half of total adult abundance

    -   female fecundity = 100 eggs

-   Assume that

```{r}
surv_tad <- surv_tad %>% 
  mutate(surv_1styr = (count * 2) / ((adults / 2) * 100)) %>% 
  summarize(mean(surv_1styr))
```
